oREVIRT analysis

### 2022-11-08 analysis/irt_analysis.Rmd
merge

```{r}
mc1 <- loo_compare(irt1, irt2, irt3)%>%as_tibble(rownames = "model")

@@

>>>>

```{r}
mc1 <- loo_compare(irt1, irt1_guess, irt2, irt3)%>%as_tibble(rownames = "model")

@@

```{r}
irt1_guess_dif_sex_sel <-  brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ sex | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_guess_dif_sex_sel, "../saves/irt1_guess_dif_sex_sel.rds")

irt1_guess_dif_sex_sel<- readRDS("../saves/irt1_guess_dif_sex_sel.rds")

```{r}
irt1_guess_dif_order_sel <- brm(
  data = irt_dat_sel,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(eta),
    eta ~ 1 + (0+ order | targetWord) + (1 | subjID),
    nl = TRUE
  ),
  prior = prior_1pl_guess,
  control = list(adapt_delta = 0.95, max_treedepth = 12),
  cores = 6,
  chains = 6,
  iter = 6000
)%>%add_criterion(c("loo","waic"))

saveRDS(irt1_guess_dif_order_sel, "../saves/irt1_guess_dif_order_sel.rds")

irt1_guess_dif_order_sel<- readRDS("../saves/irt1_guess_dif_order_sel.rds")
